Taxonomic coverage for plant data

### 2023-10-04 code/L2/L2_TropicalAndes_plant_taxcoverage.Rmd
update name

```{r}
#input trait datasets
#compare coverage of species, families, genera by trait coverage (plot)
#do the same for GBIF occurrence 
library(WorldFlora)
library(taxize)
library(BIEN)
library(GIFT)
library(dplyr)
```

# Set file paths
```{r}
data_path<-file.path('G:/Shared drives/SpaCE_Lab_FRUGIVORIA/data/plants/L0')
output_path<- file.path('G:/Shared drives/SpaCE_Lab_FRUGIVORIA/data/plants/L1')
```

>>>>

---
title: "Taxonomic coverage for plant data"
author: "Hazel J. Anderson"
project: "Plant-Frugivore Diversity"
collaborators: "Beth E. Gerstner, Phoebe L. Zarnetske"
overview: "This script summarize taxonomic coverage and gaps of plant data used."
data input: "ADD"
data output: "ADD"
date: "2023-10-04"
output: html_document
---

# Set file paths
```{r}
data_path<-file.path('G:/Shared drives/SpaCE_Lab_FRUGIVORIA/data/plants/L1')
output_path<- file.path('G:/Shared drives/SpaCE_Lab_FRUGIVORIA/data/plants/L2')
```

# Load required packages
```{r}
library(WorldFlora)
library(taxize)
library(BIEN)
library(GIFT)
library(dplyr)
```
